The Social Conditioning of Fear

### 2023-12-06 scripts/manuscript.qmd
results 1

In the absence of running models, in this section we will discuss descriptive statistics through a series of tables and plots. We seek to show how the experience of fear differed across different measures of individual-level and community-level characteristics. To begin with, across our sample of 2318 cases, mean fear was calculated at `r mean(as.numeric(overall_fear$fear, na.rm=TRUE))`.

First, we examined how fear is experienced across race and gender. As @tbl-FearRaceSex shows, Transgender and Female respondents had higher mean fear rate than respondents that identified as Male. Particularly, respondents that were Transgender expressed greater fear, but this may be indicative of sample representation. For example, only one respondent identified as both Hispanic and Transgender, and since they responded affirmative to the question, this finding is heavily skewed. When looking by race, whites were the group with the lowest mean fear and Asians were the group with the highest.

>>>>

In the absence of running models, in this section we will discuss descriptive statistics through a series of tables and plots. We seek to show how the experience of fear differed across different measures of individual-level and community-level characteristics. To begin with, across our sample of 2318 cases, mean fear was calculated at `r mean(as.numeric(overall_fear$fear, na.rm=TRUE))`. One thing to note about the interpretation of this value is, because we operationalized the variable **fear** as a dichotomous variable with answers being "Yes = 1" and "No = 0", this mean value approximates "the likelihood for an individual in our sample to report the experience of fear of walking alone at night in their neighborhood".

First, we examined how fear is experienced across race and gender. As @tbl-FearRaceSex shows, Transgender and Female respondents had higher mean fear rate than respondents who identified as Male. Particularly, respondents that were Transgender expressed greater fear, but this may be indicative of sample representation. For example, only one respondent identified as both Hispanic and Transgender, and since they responded affirmative to the question, this finding is heavily skewed. When looking by race, whites were the group with the lowest mean fear and Asians were the group with the highest. This finding is consistent with the hypothesis that the most privileged social group in terms of race has the lowest level of fear.
